---
title: "ST558 HW1: Data Science"
format: html
editor: visual
---

### Document Details

#### Author: *Smit Miyani*

#### Collaborators: *N/A*

#### Assignment: *HW1*

#### Date: *20MAY24*

#### Purpose

*General practice in working with `.qmd` files.*\

\

### Prompts

#### Prompt 1

> What do you think being a data scientist is about? *To collect, organize, analyze and visualize of large amounts of data to make informed business decisions*

#### Prompt 2

> What differences/similarities do you see between data scientists and statisticians?
>
> *Similarities*
>
> -   Both work with large amounts of data.
>
> -   Both roles require a strong foundation in mathematics and probability theory and use statistical methods to analyze data
>
> -   They often use programming languages (such as R or Python) for data manipulation and analysis.
>
> *Differences*
>
> -   Data Scientist often deal with messy, unstructured data and spend a significant amount of time cleaning and preprocessing data. On the other hand, Statisticians typically work with cleaner, well-organized data and may not need as much data cleaning
>
> -   Data Scientist work on predictive modelling whereas statisticians work on inference and experimental design

#### Prompt 3

> How do you view yourself in relation to these two areas? *I currently lean more toward the role of a statistician, but I aspire to be versatile enough to handle both data science and statistical tasks when needed.* \## Running Code

\

### Iris Data

#### `y` Object Assignment

Assigning the given code to object `y`:

```{r}
y <- density(iris$Sepal.Length)
```

Determining the class of `y` using `class()` .

```{r}
class(y)
```

Determining the object type of `y` using `typeof()` .

```{r}
typeof(y)
```

Determining the structure of `y` using `str()` .

```{r}
str(y)
```

#### Plot of `y`

Plotting the object `y` with function `plot()` . Using the `echo: false` option to ensure only output is displayed when rendered.

```{r}
#| echo: false
plot(y, main = "Sepal Length Density")
```
